\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{arev}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{}{#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%{\fontfamily{}\selectfont

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large James Tyner} &  {rusty@rtyner.com}\\
  \href{https://www.linkedin.com/in/jamestyner2}{linkedin.com/in/jamestyner2} &  863.430.2145 \\
  \href{https://github.com/rtyner}{github.com/rtyner}\\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Amazon.com}{Ruskin, FL}
      {IT Support Engineer I}{April 2018 - June 2019}
    \resumeItemListStart
        \resumeItem{}
          {Lead engineer and project manager for Cisco network lifecycle. Replaced 29 IDF cabinets with 8 stacked switches per IDF and 1500 wireless access points.}
        \resumeItem{}
          {Maintained and administered an enterprise environment consisting of 40 Linux servers, 5 Windows servers, and 300 Cisco switches.}
        \resumeItem{}
          {Led high severity incident response calls with senior management to address issues with local and global outages.}
        \resumeItem{}
          {Developed Bash and Python scripts that increased productivity and reduced human error in tasks that had previously been performed manually.}       
        \resumeItem{}
          {Introduced process improvements and drove standardization within the change management framework, reducing errors and increasing success rate of production impacting changes.}        
        \resumeItem{}
          {Trained and mentored technicians and junior team members.}
        \resumeItem{}
          {Participated in 24/7 on call rotation.}
      \resumeItemListEnd
    \resumeSubheading
      {Net-Man, Inc.}{Bartow, FL}
      {Systems Administrator}{March 2015 - April 2018}
      \resumeItemListStart
        \resumeItem{}
          {Installed, configured, and administered network and server infrastructure for over 70 SMB clients.}
         \resumeItem{}
          {Setup and managed Graylog syslog server for aggregation of firewall logs. Metrics tracked were failed VPN logins, geo-IP filtering, and content filter alerts.}
        \resumeItem{}
          {Managed backup and recovery of data, utilizing technologies such as Veeam, AWS S3, LTO, and Windows Server Backup.}
        \resumeItem{}
          {Performed physical to virtual server migrations and Windows domain migrations.}
        \resumeItem{}
          {Responsible for the deployment, updating, and configuration of physical computers, servers, and Hyper-V virtual machines in an Active Directory environment.}
        \resumeItem{}
          {Created and maintained technical documentation.}
      \resumeItemListEnd
    
    \resumeSubheading
      {Geek Squad}{Lakeland, FL}
      {Consultation Agent, Operations Agent}{July 2014 - April 2015}
      \resumeItemListStart
        \resumeItem{}
          {Leadership role involved in day to day administrative tasks.}
        \resumeItem{}
          {Responsible for maintaining morale and managing customer facing employees.}
        \resumeItem{}
          {Software installation, computer configuration, and troubleshooting.}
        \resumeItem{}
          {Oversaw shipping, receiving, scheduling, and inventory management.}
        \resumeItem{}
          {Facilitated positive customer service experience.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Homelab}{}
      {Virtualizaion Lab}{}
      \resumeItemListStart
        \resumeItem{}
          {DNS is provided by redundant BIND servers.}
        \resumeItem{}
          {Secure remote access is provded by OpenVPN.}
        \resumeItem{}
          {VMs are deployed from pre-made templates with Ansible handling the automated configuration.}
        \resumeItem{}
          {Graylog server is aggregating logs for all Linux VMs and network devices.}
        \resumeItem{}
          {Backups for the VMs are done with Bash and Python scripts.}
        \resumeItem{}
          {Network and VMs are monitored with Nagios and Grafana.}
        \resumeItem{}
          {All documentation for the lab is stored in MediaWiki running inside of a Docker container.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Polk State College}{Lakeland, FL}
      {Bachelor of Science in Information Technology}{Expected December 2020}
    \resumeSubheading
      {Polk State College}{Lakeland, FL}
      {Associate of Science in Network Infrastructure Administration}{December 2017}
    \resumeSubheading
      {Traviss Technical College}{Lakeland, FL}
      {Computer Systems \& Information Technology}{May 2014}
  \resumeSubHeadingListEnd

%-----------Technical Skills-----------------
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{}
      {Linux server administration - Debian, CentOS, and Amazon Linux}
    \resumeSubItem{}
      {Scripting - Bash, Python, and Git}
    \resumeSubItem{}
      {Change management}
    \resumeSubItem{}
      {Project management}
    \resumeSubItem{}
      {Cisco IOS configuration, management, and troubleshooting}
    \resumeSubItem{}
      {TCP/IP troubleshooting}
    \resumeSubItem{}
      {Windows Server - Active Directory, Group Policy, and WSUS}
    \resumeSubItem{}
      {Office365 Administration}
  \resumeSubHeadingListEnd
%-------------------------------------------
%}
\end{document}